Investigation of the Effect of Pretraining on EEG Classification with Deep Recurrent-Convolutional Networks

### 2017-10-15 paper/paper.tex
added network picture

Our own Model consisted of the Decoder of a trained Autoencoder for the pretrained images and a Long short-Term memory\cite{LSTM} network that classifies these representations of the Decoder. \textbf{DOES ANYBODY HAVE A GRAPHIC OF OUR WHOLE ARCHITECTURE?}

>>>>

Our own Model consisted of the encoder of a trained autoencoder for the pretrained images and a Long short-Term memory\cite{LSTM} network that classifies these representations of the decoder (see Figure \ref{fig:net_arch}).
    \includegraphics{network}
    \caption{architecture of the classifier network (left) and autoencoder (right)}\label{fig:net_arch}
